From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-07-22 dictionary.tex
Fixed the section titles.

\section{Character sheaves on \'etale commutative group schemes} \label{sec:etale}

@@

\section{Character sheaves for smooth commutative group schemes}\label{sec:main}

>>>>

\section{Character sheaves on \'etale commutative group schemes over finite fields} \label{sec:etale}

@@

\section{Character sheaves on smooth commutative group schemes over finite fields}\label{sec:main}
